\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-01-22 doc/chapters/output.tex
adding numerical values for alpha_em and alpha_s
dumping low-energy mass formulas into the manual
Still missing:
 * formatting
 * what does "heavy" mean?

At the low-scale $M_Z$ we calculate
%
\begin{align}
  \alpha_{\text{e.m.},\text{susy}}^{\text{\DRbar}}(M_Z) &=
  \frac{\alpha_{\text{e.m.},\text{SM}}^{(5),\text{\MSbar}}(M_Z)}{1 -
    \Delta\alpha_{\text{e.m.},\text{SM}}(M_Z) -
    \Delta\alpha_{\text{e.m.},\text{susy}}(M_Z)} ,\\
  \Delta\alpha_{\text{e.m.},\text{SM}}(\mu) &=
  \frac{\alpha_\text{e.m.}}{2\pi} \left[\frac{1}{3}
    - \frac{16}{9} \log{\frac{m_t}{\mu}} \right],\\
  \Delta\alpha_{\text{e.m.},\text{susy}}(\mu) &=
  \frac{\alpha_\text{e.m.}}{2\pi} \left[ -\sum_{\text{susy particle }
      i}
    C_i \log{\frac{m_i}{\mu}} \right],\\
    e_{\text{susy}}^{\text{\DRbar}}(M_Z) &=
    \sqrt{4\pi\alpha_{\text{e.m.},\text{susy}}^{\text{\DRbar}}(M_Z)}
\end{align}
%
\begin{align}
  \alpha_{\text{s},\text{susy}}^{\text{\DRbar}}(M_Z) &=
  \frac{\alpha_{\text{s},\text{SM}}^{(5),\text{\MSbar}}(M_Z)}{1 -
    \Delta\alpha_{\text{s},\text{SM}}(M_Z)
    - \Delta\alpha_{\text{s},\text{susy}}(M_Z)} ,\\
  \Delta\alpha_{\text{s},\text{SM}}(\mu) &=
  \frac{\alpha_\text{s}}{2\pi} \left[
    -\frac{2}{3} \log{\frac{m_t}{\mu}} \right],\\
  \Delta\alpha_{\text{s},\text{susy}}(\mu) &=
  \frac{\alpha_\text{s}}{2\pi}\left[ \frac{1}{2}-\sum_{\text{susy
        particle } i} C_i \log{\frac{m_i}{\mu}} \right]
\end{align}
%

>>>>

\paragraph{Gauge couplings}

At the low-scale $M_Z$ we calculate
%
\begin{align}
  \alpha_{\text{e.m.},\text{susy}}^{\text{\DRbar}}(M_Z) &=
  \frac{\alpha_{\text{e.m.},\text{SM}}^{(5),\text{\MSbar}}(M_Z)}{1 -
    \Delta\alpha_{\text{e.m.},\text{SM}}(M_Z) -
    \Delta\alpha_{\text{e.m.},\text{susy}}(M_Z)} ,\\
  \Delta\alpha_{\text{e.m.},\text{SM}}(\mu) &=
  \frac{\alpha_\text{e.m.}}{2\pi} \left[\frac{1}{3}
    - \frac{16}{9} \log{\frac{m_t}{\mu}} \right],\\
  \Delta\alpha_{\text{e.m.},\text{susy}}(\mu) &=
  \frac{\alpha_\text{e.m.}}{2\pi} \left[ -\sum_{\text{susy particle }
      i}
    C_i \log{\frac{m_i}{\mu}} \right],\\
    e_{\text{susy}}^{\text{\DRbar}}(M_Z) &=
    \sqrt{4\pi\alpha_{\text{e.m.},\text{susy}}^{\text{\DRbar}}(M_Z)}
\end{align}
%
\begin{align}
  \alpha_{\text{s},\text{susy}}^{\text{\DRbar}}(M_Z) &=
  \frac{\alpha_{\text{s},\text{SM}}^{(5),\text{\MSbar}}(M_Z)}{1 -
    \Delta\alpha_{\text{s},\text{SM}}(M_Z)
    - \Delta\alpha_{\text{s},\text{susy}}(M_Z)} ,\\
  \Delta\alpha_{\text{s},\text{SM}}(\mu) &=
  \frac{\alpha_\text{s}}{2\pi} \left[
    -\frac{2}{3} \log{\frac{m_t}{\mu}} \right],\\
  \Delta\alpha_{\text{s},\text{susy}}(\mu) &=
  \frac{\alpha_\text{s}}{2\pi}\left[ \frac{1}{2}-\sum_{\text{susy
        particle } i} C_i \log{\frac{m_i}{\mu}} \right] ,\\
  g_{3,\text{susy}}^{\text{\DRbar}}(M_Z) &=
  \sqrt{4\pi\alpha_{\text{s},\text{susy}}^{\text{\DRbar}}(M_Z)} ,
\end{align}
%
where
%
\begin{align}
  \alpha_{\text{e.m.},\text{SM}}^{(5),\text{\MSbar}}(M_Z) &= 1/127.944,\\
  \alpha_{\text{s},\text{SM}}^{(5),\text{\MSbar}}(M_Z) &= 0.1185,
\end{align}
%
are the \MSbar electromagnetic and strong cougling constants in the
Standard Model including only $5$ quark flavours
\cite{Beringer:1900zz}.  Afterwards, SARAH's tree-level expressions
for the Weinberg angle and the Hypercharge and left gauge couplings
$g_Y$ and $g_2$ in terms of $M_{W,\text{susy}}^{\text{\DRbar}}(M_Z)$,
$M_{Z,\text{susy}}^{\text{\DRbar}}(M_Z)$ and
$e_{\text{susy}}^{\text{\DRbar}}(M_Z)$ are used to calculate
$g_{1,\text{susy}}^{\text{\DRbar}}(M_Z)$ and
$g_{2,\text{susy}}^{\text{\DRbar}}(M_Z)$.  In the MSSM, for example,
we'll have
%
\begin{align}
  \theta_{W,\text{susy}}^{\text{\DRbar}}(M_Z) &=
  \arcsin\sqrt{1 - \left(\frac{M_{W,\text{susy}}^{\text{\DRbar}}(M_Z)}{M_{Z,\text{susy}}^{\text{\DRbar}}(M_Z)}\right)^2} ,\\
  g_{1,\text{susy}}^{\text{\DRbar}}(M_Z) &=
  \sqrt{\frac{5}{3}} \frac{e_{\text{susy}}^{\text{\DRbar}}(M_Z)}{\cos\theta_{W,\text{susy}}^{\text{\DRbar}}(M_Z)} ,\\
  g_{2,\text{susy}}^{\text{\DRbar}}(M_Z) &=
  \frac{e_{\text{susy}}^{\text{\DRbar}}(M_Z)}{\sin\theta_{W,\text{susy}}^{\text{\DRbar}}(M_Z)} ,
\end{align}
%
where
%
\begin{align}
  \left(M_{W,\text{susy}}^{\text{\DRbar}}(M_Z)\right)^2 &=
  \left(M_W^{\text{pole}}\right)^2 + \re \Pi_{WW}^T(p^2 = (M_W^{\text{pole}})^2) ,\\
  \left(M_{Z,\text{susy}}^{\text{\DRbar}}(M_Z)\right)^2 &=
  \left(M_Z^{\text{pole}}\right)^2 + \re \Pi_{ZZ}^T(p^2 = (M_Z^{\text{pole}})^2)
\end{align}
%
and $M_W^{\text{pole}} = 80.404\unit{GeV}$, $M_Z^{\text{pole}} =
91.1876\unit{GeV}$ \cite{Beringer:1900zz}.

\paragraph{Fermion masses}

\begin{align}
  \left(y_u^{\text{\DRbar}}(M_Z)\right)_{ij} &= \frac{\sqrt{2} m_{u,ji}}{v_u} ,\\
  \left(y_d^{\text{\DRbar}}(M_Z)\right)_{ij} &= \frac{\sqrt{2} m_{d,ji}}{v_d} ,\\
  \left(y_e^{\text{\DRbar}}(M_Z)\right)_{ij} &= \frac{\sqrt{2} m_{e,ji}}{v_e} ,
\end{align}
%
where the fermion mass matrices are given by
%
\begin{align}
  m_{u,11} &= m_{u}^{\userinput} ,\\
  m_{u,22} &= m_{c}^{\userinput} ,\\
  m_{u,33} &= m_{t,\text{susy}}^{\text{\DRbar}}(M_Z),\\
  m_{d,11} &= m_{d}^{\userinput} ,\\
  m_{d,22} &= m_{s}^{\userinput} ,\\
  m_{d,33} &= m_{b,\text{susy}}^{\text{\DRbar}}(M_Z),\\
  m_{e,11} &= m_{e}^{\userinput} ,\\
  m_{e,22} &= m_{\mu}^{\userinput} ,\\
  m_{e,33} &= m_{\tau,\text{susy}}^{\text{\DRbar}}(M_Z),\\
  m_{u,ij} &= m_{d,ij} = m_{u,ij} = 0 \quad \forall i \neq j.
\end{align}
%
Only the 3rd generation quark masses are calculated in the \DRbar
scheme from the user input quantities $m_t^\text{pole}$,
$m_{b,\text{SM}}^{\text{\MSbar}}(M_Z)$,
$m_{\tau,\text{SM}}^{\text{\MSbar}}(M_Z)$.  The top quark \DRbar mass
is calculated via
%
\begin{align}
  m_{t,\text{susy}}^{\text{\DRbar}}(\mu) &= m_t^\text{pole}
  + \re\Sigma_{tt}^{S,\text{heavy}}(m_t^\text{pole})
  + m_t^\text{pole} \left[
    \re\Sigma_{tt}^{L,\text{heavy}}(m_t^\text{pole}) +
    \re\Sigma_{tt}^{R,\text{heavy}}(m_t^\text{pole}) +
    \Delta m_t^{(1),\text{qcd}} +
    \Delta m_t^{(2),\text{qcd}}
  \right].
\end{align}
%
The QCD contributions $\Delta m_t^{(1),\text{qcd}}$ and $\Delta
m_t^{(2),\text{qcd}}$ are taken from \cite{Bednyakov:2002sf} and read
%
\begin{align}
  \Delta m_t^{(1),\text{qcd}} &= -\frac{g_3^2 \left(5-3 \log\left(\frac{m_t^2}{\mu^2}\right)\right)}{12 \pi^2},\\
  \Delta m_t^{(2),\text{qcd}} &= \left(\Delta
    m_t^{(1),\text{qcd}}\right)^2 - \frac{g_3^4 \left[396
      \log^2\left(\frac{m_t^2}{\mu^2}\right)-1476
      \log\left(\frac{m_t^2}{\mu^2}\right)-48 \zeta(3)+2011+16 \pi ^2
      (1+\log(4))\right]}{4608 \pi^4}.
\end{align}
%
The \DRbar mass of the bottom quark is calculated via
\cite{Baer:2002ek}
%
\begin{align}
  m_{b,\text{susy}}^{\text{\DRbar}}(\mu) &=
  \frac{m_{b,\text{SM}}^{\text{\DRbar}}(\mu)}{1 -
    \re\Sigma_{bb}^{S,\text{heavy}}(m_{b,\text{SM}}^\text{\MSbar})/m_b
    - \re\Sigma_{bb}^{L,\text{heavy}}(m_{b,\text{SM}}^\text{\MSbar}) -
    \re\Sigma_{bb}^{R,\text{heavy}}(m_{b,\text{SM}}^\text{\MSbar})} ,\\
  m_{b,\text{SM}}^{\text{\DRbar}}(\mu) &=
  m_{b,\text{SM}}^{\text{\MSbar}}(\mu) \left(1 - \frac{\alpha_s}{3
      \pi} - \frac{23}{72} \frac{\alpha_s^2}{\pi^2} + \frac{3
      g_2^2}{128 \pi^2} + \frac{13 g_1^2}{1152 \pi^2}\right) .
\end{align}
%
The \DRbar mass of the $\tau$ is calculated via
%
\begin{align}
  m_{\tau,\text{susy}}^{\text{\DRbar}}(\mu) &=
  m_{\tau,\text{SM}}^{\text{\DRbar}}(\mu) +
  \re\Sigma_{\tau\tau}^{S,\text{heavy}}(m_{\tau,\text{SM}}^\text{\MSbar}) +
  m_{\tau,\text{SM}}^{\text{\DRbar}}(\mu) \left[
    \re\Sigma_{\tau\tau}^{L,\text{heavy}}(m_{\tau,\text{SM}}^\text{\MSbar}) +
    \re\Sigma_{\tau\tau}^{R,\text{heavy}}(m_{\tau,\text{SM}}^\text{\MSbar})
  \right] ,\\
  m_{\tau,\text{SM}}^{\text{\DRbar}}(\mu) &= m_{\tau,\text{SM}}^{\text{\MSbar}}(\mu)
  \left(1 - 3 \frac{g_1^2 - g_2^2}{128 \pi^2}\right).
\end{align}
